---
title: "p8105_hw5_tw2838"
author: "Tianyou Wang"
date: "2022-11-16"
output: html_document
---

## Setting Opotions

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



# Problem #1 A Longitudinal Study

Code is downloaded from the partial solution provided by professor.

In the following code chunk, data in individual spreadsheets are combined in one dataframe `full_df`.

```{r message=FALSE, warning=FALSE}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```


This R code chunk below transfer the wide format into long format. Only the "group", "subject", "week" and "outcome" are presented. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way.




# Problem #2 A Homicides in 50 Large U.S. Cities

### *Data cleaning*

Import and clean the homicides csv file.

```{r message=FALSE, warning=FALSE}
hom_df = read_csv("./data/homicide-data.csv") %>%
  janitor::clean_names() 
```

The raw homicides dataset includes `r nrow(hom_df)` observations and `r ncol(hom_df)` variables, including `r variable.names(hom_df)`. Each row contains information for one case of homicides. 


```{r message=FALSE, warning=FALSE}
hom_df = hom_df %>%
  mutate(city_state = str_c(city, state, sep = ","),
         solve_status = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state, solve_status)

summary_df = hom_df %>%
  group_by(city_state) %>% 
  summarise(n_hom = n(),
            n_unsolve = sum(solve_status == "unsolved"))

knitr::kable(summary_df)
```

The code chunck above did:

* created the `city_state` variable that include the city and state information by using `city_state = str_c()`
* created the `solve_status` variable that indicate whether the homicide case is solved or unsolved
* obtained the total number of homicides within each cities
* obtained the number of unsolved homicides within each cities


### *Estimate the proportion of unsolved homicides in Baltimore, MD*

```{r message=FALSE, warning=FALSE}
bal_df = summary_df %>% 
  filter(city_state == "Baltimore,MD")

test_output = prop.test(
  x = pull(bal_df, n_unsolve),
  n = pull(bal_df, n_hom)) %>% 
  broom::tidy()

list(
  proportion = round(test_output$estimate, 3),
  CI = str_c(round(test_output$conf.low, 3), 
             round(test_output$conf.high, 3)))
```

By using the `prop.test` function, we estimated the proportion of unsolved homicides in the city of Baltimore, MD, is `r round(test_output$estimate, 3)*100`% (95% CI: `r round(test_output$conf.low, 3)*100`%, `r round(test_output$conf.high, 3)`%).


### *Estimate the proportion of unsolved homicides in each city*

```{r message=FALSE, warning=FALSE}
city_test = summary_df %>% 
  mutate(prop_test = map2(n_unsolve, n_hom, ~prop.test(.x, .y) %>% 
     broom::tidy())) %>%
    unnest() %>%
  select(city_state, estimate, conf.low, conf.high)

city_test
```

### *Create a plot that shows the estimates and CIs for each city*

```{r}
city_test %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point(col=2) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 270, hjust=0))
```


# Problem #3 Simulation: Explore Power in a One-Sample t-Test



